---
title: "Feb 5 (Assignment)"
output: html_document

```

## Read the data set
```{r}
data = read.csv( "https://www.stats.govt.nz/assets/Uploads/Government-finance-statistics-general-government/Government-finance-statistics-general-government-Year-ended-June-2020/Download-data/government-finance-statistics-general-government-year-ended-june-2020-csv.csv" 
stringAsFacrors = TRUE)
data
head(data)
## to find the data types of the variables
str(data)
```
```{r}
## create a 3*3 Matrix
A = matrix(c(4, 5, 7, 8, 0, 9, 5, 4, 8) ,3, 3)
A
#transpose
A_transpose = t(A)
A_transpose
```
```{r}
## Create a new matrix of same order naming it as B
B = matrix(c(14, 52, 75, 89, 10, 91, 51, 44, 28),3, 3 )
B
#Addition of two matrix A and B
A + B
# Subtraction 
A - B

#Multipilcation
A * B

#DIVISION
A / B
```
```{r}
#performing vector operations
V1 = c(1, 2, 3, 4, 5, 6, 7)
V2 = c(7, 6, 5, 4, 3, 2, 1)
V1
V2

V1 + V2
V1 - V2
V1 * V2
V1 / V2

cbind(V1, V2)

rbind(V1)

as.numeric(V1)

as.character(V1)
``
```{r}
employee_data <- data.frame(
  employee_id = c (1:8),
  employee_name = c("RICK","DAN","MICHELLE","RYAN","GARY","NINA", "SIMON","GURU"),
  salary = c(623.3,515.2,611.0,729.0,843.25,578,632.8,722.5),
  start_date = as.Date(c("2012-01-01", "2013-09-23", "2014-11-15", "2014-05-11","2015-03-27", "2013-05-21", "2013-07-30", "2014-06-17"),
  dept = c("IT","OPERATIONS","IT","HR","FINANCE","IT","OPERATIONS","FINANCE")),
  stringsAsFactors = FALSE)
  employee_data
print(employee_data)
```
```{r}
#import libraries
```
  





 