---
title: " World cup data"


output: html_notebook
---

. 

```{r}
library(readr)
world_cup_comparisons <- read_csv("world cup data/world_cup_comparisons.csv")
head(world_cup_comparisons)
```
```{r}
str(world_cup_comparisons)
```


```{r}
dim(world_cup_comparisons)
```
```{r}
summary(world_cup_comparisons)
```
```{r}
##Checking missing values
is.na(world_cup_comparisons)
summary(is.na(world_cup_comparisons))
colSums(is.na(world_cup_comparisons))
```

```{r}
##identifying less than 3 values
any(world_cup_comparisons$goals_z>3)
any(world_cup_comparisons$aerials_z>3)
any(world_cup_comparisons$passes_z>3)
```
```{r}
library(ggplot2)
library(caret)
library(caretEnsemble)
library(VIM)
library(gridExtra)
library(cowplot)
library(data.table)
library(corrplot)
library(e1071)
library(xgboost)
```

```{r}
## Relation ship between goals_z and season
library(ggplot2)
ggplot(world_cup_comparisons, aes(x= goals_z, y = season)) + 
  geom_point(size = 1, color="black") + 
  xlab("goals_z ") + ylab("season") + 
  ggtitle("goals_z  vs season ") 
  theme_linedraw()
```
```{r}
# fouls_z vs season
ggplot(world_cup_comparisons, aes(fouls_z, season)) + 
  geom_bar( stat = "identity",color = "blue") +
  theme(axis.text.x = element_text(angle = 70, vjust = 2, color = "navy")) + 
  xlab("fouls_z") + ylab("season")+
  ggtitle("fouls_z  vs season") +
  theme_linedraw()
  ggtitle("fouls_z vs season") + theme_bw()
```
```{r}
ggplot(world_cup_comparisons, aes(interceptions_z, season)) + 
  geom_bar( stat = "identity",color = "blue") +
  theme(axis.text.x = element_text(angle = 70, vjust = 2, color = "navy")) + 
  xlab("interceptions_z") + ylab("season")+
  ggtitle("interceptions_z  vs season") +
  theme_linedraw()
```
```{r}
ggplot(world_cup_comparisons, aes(boxtouches_z, season)) + 
  geom_bar( stat = "identity",color = "blue") +
  theme(axis.text.x = element_text(angle = 70, vjust = 2, color = "navy")) + 
  xlab("boxtouches_z") + ylab("season")+
  ggtitle("boxtouches_z  vs season") +
  theme_linedraw()
```

##spliting data sets into "training" (80%) and "testing"(20%)
```{r}
ind <- sample(2, nrow(world_cup_comparisons),replace = TRUE, prob = c(0.8,0.2))
training_data <- world_cup_comparisons[ind==1,]
testing_data <- world_cup_comparisons[ind==2,]
head(training_data)
head(testing_data)

```
```{r}
#Checking Dim of test and train data
dim(training_data)
dim(testing_data)
```
```{r}
# combine the data sets.

combi <- rbind(training_data, testing_data)
dim(combi)
```
### Impute missing value 

```{r}
#Impute missing value by median
combi$passes_z [is.na(combi$passes_z )] <- median(combi$passes_z , na.rm = TRUE)
combi$passes_z [is.na(combi$passes_z )]
table(is.na(combi$passes_z ))
```
```{r}
combi$goals_z [is.na(combi$goals_z )] <- median(combi$goals_z , na.rm = TRUE)
combi$goals_z [is.na(combi$goals_z )]
table(is.na(combi$goals_z ))
```
```{r}
combi$xg_z [is.na(combi$xg_z )] <- median(combi$xg_z , na.rm = TRUE)
combi$xg_z [is.na(combi$xg_z )]
table(is.na(combi$xg_z ))
```
```{r}
combi$crosses_z [is.na(combi$crosses_z )] <- median(combi$crosses_z , na.rm = TRUE)
combi$crosses_z [is.na(combi$crosses_z )]
table(is.na(combi$crosses_z ))
```

```{r}
combi$boxtouches_z [is.na(combi$boxtouches_z )] <- median(combi$boxtouches_z , na.rm = TRUE)
combi$boxtouches_z [is.na(combi$boxtouches_z )]
table(is.na(combi$boxtouches_z ))
```

```{r}
combi$progpasses_z [is.na(combi$progpasses_z )] <- median(combi$progpasses_z , na.rm = TRUE)
combi$progpasses_z [is.na(combi$progpasses_z )]
table(is.na(combi$progpasses_z ))
```
```{r}
combi$takeons_z  [is.na(combi$takeons_z  )] <- median(combi$takeons_z  , na.rm = TRUE)
combi$takeons_z  [is.na(combi$takeons_z  )]
table(is.na(combi$takeons_z  ))
```
```{r}
combi$progruns_z  [is.na(combi$progruns_z )] <- median(combi$progruns_z  , na.rm = TRUE)
combi$progruns_z  [is.na(combi$progruns_z  )]
table(is.na(combi$progruns_z  ))
```
```{r}
combi$tackles_z  [is.na(combi$tackles_z)] <- median(combi$tackles_z  , na.rm = TRUE)
combi$tackles_z  [is.na(combi$tackles_z  )]
table(is.na(combi$tackles_z  ))
```
```{r}
combi$interceptions_z  [is.na(combi$interceptions_z)] <- median(combi$interceptions_z  , na.rm = TRUE)
combi$interceptions_z  [is.na(combi$interceptions_z )]
table(is.na(combi$interceptions_z ))
```
```{r}
combi$clearances_z  [is.na(combi$clearances_z)] <- median(combi$clearances_z  , na.rm = TRUE)
combi$clearances_z  [is.na(combi$clearances_z )]
table(is.na(combi$clearances_z ))
```
```{r}
combi$blocks_z [is.na(combi$blocks_z)] <- median(combi$blocks_z  , na.rm = TRUE)
combi$blocks_z  [is.na(combi$blocks_z )]
table(is.na(combi$blocks_z))
```

```
```{r}
combi$aerials_z[is.na(combi$aerials_z)] <- median(combi$aerials_z  , na.rm = TRUE)
combi$aerials_z  [is.na(combi$aerials_z )]
table(is.na(combi$aerials_z))
```
```{r}
summary(combi)
```
```{r}
glimpse(world_cup_comparisons)
```
Imputing Missing Values
```{r}
#Using kNN imputation for missing values
world_cup_comparisons_imputed <- kNN(world_cup_comparisons)
world_cup_comparisons_imputed <- world_cup_comparisons_imputed %>% 
    select(nsxg_z :player)
summary(world_cup_comparisons_imputed)
summary(is.na(world_cup_comparisons_imputed))
```
# Visualizing Data
```{r}
# World cup Season comparison Boxplot
ggplot(world_cup_comparisons_imputed, aes(x =aerials_z ,y = season)) +
  geom_boxplot() +
  labs(title = "season by aerials_z", x = "aerials_z", y = "season") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
ggplot(world_cup_comparisons_imputed, aes(x =interceptions_z ,y = season)) +
  geom_bin2d() +
  facet_wrap(~ boxtouches_z) +
  labs(title = "season by interceptions_z and boxtouches_z",
       x = "interceptions_z",
       y = "season")
```
```{r}


